### 2025-04-17 multiple-regression.qmd
20250417 - fixes and references

To evaluate for potential nonlinearity in the associations, we can also evaluate residual plots (@fig-residualPlots), marginal model plots (@fig-marginalModelPlots), and added-variable plots (@fig-addedVariablePlots), and component-plus-residual plots (@fig-componentPlusResidualPlots) from the `car` package [@Fox2019_packages; @R-car].
For evaluating linearity, we would expect minimal bend/curvature in the lines.

@@

hist(
  log(player_stats_seasonal$target_share[which(player_stats_seasonal$position == "WR")] + 1),
  "Histogram of Target Share (Log Transformed)")
```

@@

@@

To evaluate homoscedasticity, we can evaluate a residual plot (@fig-residualPlots) and spread-level plot (@fig-spreadLevelPlots).
In a residual plot, you want a constant spread of residuals versus fitted values—you do not want the residuals to show a fan or cone shape.

>>>>

To evaluate for potential nonlinearity in the associations, we can also evaluate residual plots (@fig-residualPlots), marginal model plots (@fig-marginalModelPlots), added-variable plots (@fig-addedVariablePlots), and component-plus-residual plots (@fig-componentPlusResidualPlots) from the `car` package [@Fox2019_packages; @R-car].
For evaluating linearity, we would expect minimal bend/curvature in the lines.

@@

hist(
  log(player_stats_seasonal$target_share[which(player_stats_seasonal$position == "WR")] + 1),
  main = "Histogram of Target Share (Log Transformed)")
```

@@

When creating a residual plot, the `car` package [@Fox2019_packages; @R-car] also provides a test of the nonlinearity of each [predictor](#sec-correlationalStudy).

@@

To evaluate homoscedasticity, we can evaluate a residual plot (@fig-residualPlots) and spread-level plot (@fig-spreadLevelPlots) from the `car` package [@Fox2019_packages; @R-car].
In a residual plot, you want a constant spread of residuals versus fitted values—you do not want the residuals to show a fan or cone shape.
